Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension

### 2018-05-29 EMNLP-demo-paper/result.tex
added model description, very brief
add prediction section
update structure

\section{Application Results}

\subsection{Natural Language Inference}
We demonstrate our visualization system on the decomposable attention networks
for NLI task. The goal is that, given a premise sentence and a hypothesis sentence,
predict their relation as one of \emph{Entailment, Contradiction, Neutral}.
The model can be formalized as the following:
\begin{align}
	P^\prime, H^\prime &= f(P), f(H)\\
	\overleftarrow{A} &= P^\prime \cdot H^\prime\\
	\overrightarrow{A} &= H^\prime \cdot P^\prime\\
	y &= g(P, H, P^\prime, H^\prime, \overleftarrow{A}, \overrightarrow{A})
\end{align}
where $P$ and $H$ are input embedding matrices for the premise and the hypothesis, $\overleftarrow{A}$
and $\overrightarrow{A}$ are attentions, and $y$ is the predicted probabilities for candidate classes.
Our system visualized the bidirectional attentions and their interaction with output distribution over labels.

\subsection{Machine Comprehension}
In machine comprehension task, two sequences of texts are given: context and question.
The target is to select a span of text from the context that answers the question. We provide a simple model
formulation and refer the reader to the paper for details.
\begin{align}
	C^\prime, Q^\prime &= BiLSTM(C), BiLSTM(Q)\\
	\overleftarrow{A} &= u(C^\prime, Q^\prime)\\
	\overrightarrow{A} & v(C^\prime, Q^\prime)\\
	s &= m(C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})\\
	e &= n(s, C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})
\end{align}
where $C$ and $Q$ are embedding matrices for the context and the question,
$\overleftarrow{A}$ and $\overrightarrow{A}$ are bidirectional attention flows,
$s$ and $e$ are probabilities for starting and ending indices of the answer span.
Our system reveals the internal states of $\overleftarrow{A}$, $\overrightarrow{A}$,
$s$ and $e$.

>>>>

\section{Application}
We demonstrate our visualization system on the decomposable attention networks
for natural language inference task, and the bi-directional attention flow for the machine comprehension task.

\subsection{Natural Language Inference}
Given a premise sentence and a hypothesis sentence,
predict their relation as one of \emph{Entailment, Contradiction, Neutral}.
The model can be formalized as the following:
\begin{align}
	P^\prime, H^\prime &= f(P), f(H)\\
	\overleftarrow{A} &= P^\prime \cdot H^\prime\\
	\overrightarrow{A} &= H^\prime \cdot P^\prime\\
	y &= g(P, H, P^\prime, H^\prime, \overleftarrow{A}, \overrightarrow{A})
\end{align}
where $P$ and $H$ are input embedding matrices for the premise and the hypothesis, $\overleftarrow{A}$
and $\overrightarrow{A}$ are attentions, and $y$ is the predicted probabilities for candidate classes.
Our system visualized the bidirectional attentions and their interaction with output distribution over labels.

\subsection{Machine Comprehension}
In machine comprehension task, two sequences of texts are given: context and question.
The target is to select a span of text from the context that answers the question. We provide a simple model
formulation and refer the reader to the paper for details.
\begin{align}
	C^\prime, Q^\prime &= BiLSTM(C), BiLSTM(Q)\\
	\overleftarrow{A} &= u(C^\prime, Q^\prime)\\
	\overrightarrow{A} &= v(C^\prime, Q^\prime)\\
	s &= m(C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})\\
	e &= n(s, C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})
\end{align}
where $C$ and $Q$ are embedding matrices for the context and the question,
$\overleftarrow{A}$ and $\overrightarrow{A}$ are bidirectional attention flows,
$s$ and $e$ are probabilities for starting and ending indices of the answer span.
Our system reveals the internal states of $\overleftarrow{A}$, $\overrightarrow{A}$,
$s$ and $e$.

### 2018-05-29 EMNLP-demo-paper/system.tex
update structure

#initialize machine comprehension model
model = bidafModelInterface(
    wordDict="data/bidaf/squad.word.dict",
    wordVec="data/bidaf/glove.hdf5",
    model="data/bidaf/bidaf.ema")

gen = translationPerturbation()

# visualization components
visLayout = {
  "column":[{"row": ["Paragraph", 
                     "AttentionSubMatrix"]},
            {"row": ["AttentionAsymmetric"]}]
  }

#setup interface
modelVis = MCModule(visLayout)

modelVis.setPredictionHook(model.predict)
modelVis.setAttentionHook(model.attention)
modelVis.setSentenceHook(gen.perturbSentence)

#open browser for the web-based visualization
modelVis.show()
\end{lstlisting}

>>>>

#initialize machine comprehension model
model = bidafModelInterface(
    wordDict="data/bidaf/squad.word.dict",
    wordVec="data/bidaf/glove.hdf5",
    model="data/bidaf/bidaf.ema")
gen = translationPerturbation()
#visualization components
visLayout = {
  "column":[{"row": ["Paragraph", 
                     "AttentionSubMatrix"]},
            {"row": ["AttentionAsymmetric"]}]
  }
#setup interface
modelVis = MCModule(visLayout)
modelVis.setPredictionHook(model.predict)
modelVis.setAttentionHook(model.attention)
modelVis.setSentenceHook(gen.perturbSentence)
#open browser for the web-based visualization
modelVis.show()
\end{lstlisting}
